Finding Optimal Sequences for Area Aggregation ---\protect\\ \Astar vs. Integer Linear Programming

### 2019-02-27 area_agg_seq_tsas.tex
moved materials from my thesis to this paper

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
We approach this problem for land-cover maps.
%Given two maps of the same region at two different scales,
%a relevant problem is to compute maps for any intermediate scale.
Given two land-cover maps at two different scales, 
we want to find a sequence of small incremental
% To help map users not to lose context during zooming,
% we try to provide maps that change as continuous as possible.
% Since maps at some different scales often exist, 
% a relevant problem is to find maps at any intermediate scales.
% Given two land-cover maps of different scales, 
% we wish to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of polygons on the larger-scale map.

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
%We compared the \Astar algorithm and 
%integer linear programming in solving this problem.
For solving such a problem, standard approaches
are the \Astar algorithm or integer linear programming.
%We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

Maps are the main tool to represent geographical information. 
As geographical information is usually scale-dependent
\parencite{Muller1995Generalization,Weibel1997}, 
users need to have access to maps at different scales.
In our digital age, people realize this access by zooming on 
computers or mobile phones.
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
A naive solution is 
to switch between maps at different scales.
This method, however, can result in 
large discrete changes, 
which tend to distract users.
A more advanced strategy is  
\emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which emphasizes on generalizing in real time.
Still, large discrete changes can be introduced.
To have a better zooming experience, 
users prefer the changes to be continuous.
This is why some digital maps such as Google Maps 
are trying to make zooming as continuous as they can,
though Google Maps is still based on switching between 
a certain number of maps at different scales.
The process of producing maps at any different scales
with smooth changes 
is called \emph{continuous map generalization} (CMG).
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area, 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} presented a method for computing an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land cover areas become too small to be seen.
These areas have to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as good as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{smallest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then we can say that the model is not reasonable.
In this case, we should try another model, say, 
to minimize the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

Optimization has been widely used in map generalization.
For example, \textcite{Harrie1999} displaced objects 
based on least-squares adjustments (LSA)
to solve spatial conflicts.
In his problem, the soft constraints 
for shapes and locations may contradict each other.
Therefore, it is necessary 
to mediate between these constraints, 
which is done by LSA.
\textcite{Sester2005Optimization} used LSA not only for 
displacing objects, but also for simplifying buildings. 
The output boundaries are required to 
be as close as possible to the original buildings.
\textcite{Tong2015AreaLSA} generalized land-cover areas,
where LSA was used to preserve the sizes of 
the land-cover areas.
\textcite{Regnauld2001} grouped buildings based on 
minimum spanning trees in order to typify
the buildings in a group.
\textcite{Burghardt2005Snakes} smoothed lines based on 
energy minimization. 
According to his setting, a line contains less energy
if it is smooth and close to the original line.
He repeatedly displace the line 
until finding a stable state 
in terms of minimizing his energy function.
\textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
based on mixed-integer linear programming.
This method is based on global optimization and minimizes 
type changes as well as a cost for non-compact shapes 
while satisfying constraints on the sizes of the output regions.
\textcite{Haunertwolff2010Building} simplified building
footprints by solving an integer linear program (ILP).
They aimed at minimizing the number of edges in the output under 
the restriction that the simplified buildings must be 
topologically safe,
that is, the selected and extended edges must not intersect with 
each other.
\textcite{Oehrlein2017Aggregation} aggregated the departments 
of France according to the unemployment rates based on integer 
linear programming; they used a cutting-plane method to 
speed up solving their ILP.
\textcite{Funke2017Simplification} simplified 
administrative boundaries based on an ILP.
Their aim was to minimize the number of edges
while keeping the result boundaries close to the original ones
and avoiding any intersection. 
At the same time, every city, which is represented by a point, 
stays in the same face as before.

%\todo{may cite \textcite{Bader2001Dissertation}}

\mypar{Optimization in \emph{continuous} map generalization}
Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map, 
but also for relations between maps. 
%
Nevertheless, some optimization techniques 
have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that 
a point, once disappeared, should not show up again 
during zooming out, 
and that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for the given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks, at each step.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

\mypar{Problem definition}
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
tiny polygons, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we want to remove these tiny polygons.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split these tiny parcels 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.
However, our method does not consider splitting.
We focus on aggregating areas.
A \emph{land-cover map} is a planar subdivision in which each 
area belongs to a
land-cover class or \emph{type}.
Suppose that there are two land-cover maps of 
different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes 
that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

With the same motivation, a strategy of hierarchical schemes 
has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree 
(GAP-tree),
which can be constructed if only the larger-scale map is given
\citep{vanOosterom1995Development} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, 
in a greedy fashion.  
If we insist on finding a sequence that is, 
according to some global measure, optimal, 
the problem becomes complicated.

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
that aggregate land-cover areas
result in many-to-one relationships.
The input and the generalized results of these methods 
can be used as our input.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, with the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single output scale, 
given a land-cover map at a larger scale.
Although the method of \textcite{HaunertWolff2010AreaAgg}
leads to results of high quality, 
it does not yield land-cover maps at intermediate scales.

To generate a good sequence of maps, 
we must consider the sequence of maps as a whole 
instead of considering each intermediate-scale map independently.
To simplify the problem,
we first consider each region of the goal map 
(with its components on the start map) 
independently of the other regions.
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence 
that transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

%\todo{may cite \textcite{Suba2014Merge}}

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an integer linear program, 
and then solve this program, minimizing our cost function.
Our linear program uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a data set of the German topographic database ATKIS 
(see \sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

We do not deal with the simplification of lines in this paper, 
since this can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973,Saalfeld1999,Wu2004DP}.
Those methods can be used to set up 
the binary line generalized (BLG) tree
\citep{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.

@@

We show how to compute an aggregation sequence for one region. 
For a goal map with many regions, 
after having found a sequence for each of them
we ``interleave'' these aggregation sequences
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
merge sort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
\centering
\includegraphics[page=1]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

>>>>

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
We approach this problem for land-cover maps.
Given two land-cover maps at two different scales, 
we want to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of adjacent polygons 
on the larger-scale map.

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
We present the \Astar algorithm and integer linear programming
to solve this optimization problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm as a benchmark.
We tested the three methods with a
dataset of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

Maps are the main tool to represent geographical information. 
As geographical information is usually scale-dependent
\parencite{Muller1995Generalization,Weibel1997}, 
users need to have access to maps at different scales.
In order to generate these maps,
national mapping agencies produce a base map
and then derive maps at smaller scales by 
\emph{map generalization}
More specifically, 
map generalization is the process of extracting and arranging
geographical information from detailed data in order to produce maps
at smaller scales.
A requirement of map generalization is to emphasize the 
essential while suppress the unimportant,
and at the same time maintain logical relationship between 
objects \parencite{Weibel1997}.
As manual generalization is labor-intensive
\parencite{Duchene2014},
automating map generalization is a promising way 
to produce up-to-date maps at high speed and low cost 
\parencite{Mackaness2017Generalization}.

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{greatest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then the model may be not reasonable.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

Optimization has been widely used in map generalization.
For example, \textcite{Harrie1999} displaced objects 
based on least-squares adjustments (LSA)
to solve spatial conflicts.
In his problem, the soft constraints 
for shapes and locations may contradict each other.
Therefore, it is necessary 
to mediate between these constraints, 
which can be done by LSA.
\textcite{Sester2005Optimization} used LSA not only for 
displacing objects but also for simplifying buildings. 
She required that 
the output boundaries should be 
as close to the original buildings as possible.
\textcite{Tong2015AreaLSA} generalized land-cover areas,
where LSA was used to preserve the sizes of 
the land-cover areas.
\textcite{Regnauld2001} grouped buildings based on 
minimum spanning trees in order to typify
the buildings in a group.
\textcite{Burghardt2005Snakes} smoothed lines based on 
energy minimization. 
According to his setting, a line contains less energy
if it is smooth and close to the original line.
He repeatedly displaced the line 
until a stable state 
in terms of minimizing his energy function is found.
\textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
based on mixed-integer linear programming
to generate a map at a target scale.
Their method is based on a global optimization.
They minimize a combination of type changes and cost for non-compact shapes 
while satisfying constraints on the sizes of the output regions.
\textcite{Haunertwolff2010Building} simplified building
footprints by solving an integer linear program (ILP).
They aimed at minimizing the number of edges in the output 
under the restriction that 
the simplified buildings must be topologically safe,
that is, the selected and extended edges must not intersect with 
each other.
\textcite{Oehrlein2017Aggregation} aggregated the departments 
of France according to unemployment rates based on integer 
linear programming; they used a cutting-plane method to 
speed up solving their ILP.
\textcite{Funke2017Simplification} simplified 
administrative boundaries based on an ILP.
Their aim was to minimize the number of edges
while keeping the result boundaries close to the original ones
and avoiding any intersection. 
At the same time, they required that every city, 
represented by a point, 
stays in the same face as before the generalization.

\mypar{Optimization in \emph{continuous} map generalization}
Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map
but also for relations between maps at difference scales. 
%
Some optimization techniques have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that a point, once disappeared, 
should not show up again during zooming out. 
They also required that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for a given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks of all the steps.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

\mypar{Problem definition}
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.
A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

With the same motivation, 
a strategy of hierarchical schemes has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree (GAP-tree).
This tree can be constructed if only the larger-scale map is given
\citep{vanOosterom1995Development} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, in a greedy fashion.  
If we insist on finding a sequence that is optimal 
according to some global measure,
the problem becomes complicated.

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
that aggregate land-cover areas
result in many-to-one relationships.
Their inputs and generalized results together
can be used as our inputs.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce land-cover maps at intermediate scales.

In this chapter, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

We do not deal with simplifying polylines in this chapter.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
%
Although splitting polygons is a good step
of generalizing land-cover areas,
we do not integrate it into our method at this moment.
Some examples of splitting are as follows.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split tiny polygons 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on a constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.

@@

We show how to compute an aggregation sequence 
for a single region, $R$. 
For a goal map with many regions,
we ``interleave'' the sequences for each of them
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
Mergesort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors (adjacent areas)~$v$
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function.
This requirement ensures that the 
size of the smallest area on the map increases in each step.
Hence, the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
we consider the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces 
the number of possible solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.
